### 2016-04-19 thesis_paper/source.tex
paper stuff

@@

@@

\begin{abstract}
\justify
Modern simulation systems generate big amount of data, which consequently has to be analyzed in a timely fashion. Traditional database management systems follow principle of pulling the needed data, processing it, and then returning the results. This approach is then optimized by means of caching, storing in different structures, or doing some sacrifices on precision of the results to make it faster. When it comes to the point of doing various queries that require analysis  of the whole data,  this design has the following disadvantages: considerable overhead on random I/O while reading from the simulation output files and low throughput of the data that consequently results in long latency, and, if there was any indexing to optimize selections, overhead of storing those becomes too big, too.

@@

Big data processing is becoming one of the key issues with the amount of data being generated by modern systems. Eventually, this data is required to be processed on the fly, thus, analysis software should be able to handle massive data in a very short period of time. When working with huge volume of data, there are non-trivial issues arise. For example, it can take days and weeks to analyze big enough data sets, because the data cannot be simply loaded into memory, since it can get up to terabytes, thus, it has extra overhead because of widely used random access disk I/O framework to read from disk chunks by chunks. Besides it, analysis of the data can get even more complicated, since going through certain parts of the data once would not be enough, which leads to low throughput and efficiency of loaded data. One such example, the data analysis approach has polynomial complexity just for reading the data in order to come up with result, and since the data can't simply be saved in memory, it raises the overhead of disk I/O, too. Pull-based architectures in data processing engines are inefficient, since having a set of specific queries, in order to compute them all, it is needed to fetch data, filter it, and apply needed formulas. It is inefficient, since for every query the same chunk of data needs to be pulled into the memory at least the number of queries times or more in case of more complex queries.

As it has already been mentioned in the previous paper \cite{mainPaper}, one of the modern issues of analyzing massive data on the fly is social networks. .
"In order for a system to be able to perform analytical examination of the data produced in such streaming media, the system should have the capability of fast data access. The reason, the millions of data records(tweets) produced
every second. Moreover, these tweets may have
different geographical origin, introducing different languages and
forms and often times containing unsolicited messages, errors,
malicious content, etc. Therefore, some low level data uniformity
and cleaning on top of the data access and management issues should
be considered and possibly incorporated in the process of analytical
investigation in order to achieve relevant result. "\cite{mainPaper, nature_bigdata08,nature_bigdata12,science_social10,jcs_twitter11}

@@

\begin{figure}
 \centerline{ \includegraphics[width=1\columnwidth]{images/speedup838K-pomalo-za-4.eps} }
 \caption{ Speed up over different levels of atom selection for 838,400 atoms \cite{mainPaper}}
 \label{fg:sample_estimation_old_paper}
\end{figure}

>>>>

\newgeometry{left=20mm,right=20mm,top=35mm,bottom=35mm}

@@

\clearpage
\restoregeometry

@@

\begin{abstract}
\justify
\hspace{3em} Modern simulation systems generate big amount of data, which consequently has to be analyzed in a timely fashion. Traditional database management systems follow principle of pulling the needed data, processing it, and then returning the results. This approach is then optimized by means of caching, storing in different structures, or doing some sacrifices on precision of the results to make it faster. When it comes to the point of doing various queries that require analysis  of the whole data,  this design has the following disadvantages: considerable overhead on random I/O while reading from the simulation output files and low throughput of the data that consequently results in long latency, and, if there was any indexing to optimize selections, overhead of storing those becomes too big, too.

@@

Big data processing is becoming one of the key issues with the amount of data being generated by modern systems. Eventually, this data is required to be processed on the fly, thus, analysis software should be able to handle massive data in a very short period of time. When working with huge volume of data, there are non-trivial issues arise. For example, it can take days and weeks to analyze big enough data sets, because the data cannot be simply loaded into memory, since it can get up to terabytes, thus, it has extra overhead because of traditional random access disk I/O framework to read from disk chunks by chunks. Besides it, analysis of the data can get even more complicated, since going through certain parts of the data once would not be enough, which leads to low throughput and efficiency of loaded data. One such example, the data analysis approach has polynomial complexity just for reading the data in order to come up with result, and since the data can't simply be saved in memory, it raises the overhead of disk I/O, too. Pull-based architectures in data processing engines are inefficient, since having a set of specific queries, in order to compute them all, it is needed to fetch data, filter it, and apply needed formulas. It is inefficient, since for every query the same chunk of data needs to be pulled into the memory at least the number of queries times or more in case of more complex queries.

As it has already been mentioned in the previous paper \cite{mainPaper}, one of the modern issues of analyzing massive data on the fly is social networks. "In order for a system to be able to perform analytical examination of the data produced in such streaming media, the system should have the capability of fast data access. The reason, the millions of data records (tweets) produced every second. Moreover, these tweets may have different geographical origin, introducing different languages and forms and often times containing unsolicited messages, errors,
malicious content, etc. Therefore, some low level data uniformity
and cleaning on top of the data access and management issues should
be considered and possibly incorporated in the process of analytical
investigation in order to achieve relevant result. "\cite{mainPaper, nature_bigdata08,nature_bigdata12,science_social10,jcs_twitter11}

@@

\begin{figure}
 \centerline{ \includegraphics[width=0.5\columnwidth]{images/speedup838K-pomalo-za-4.eps} }
 \caption{ Speed up over different levels of atom selection for 838,400 atoms \cite{mainPaper}}
 \label{fg:sample_estimation_old_paper}
\end{figure}
